---
title: "brennas_OriginalHomeworkCode_01"
author: "brennastallings"
date: "9/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Challenge 1


```{r Ulysses}
##First, create a vector of 1 word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”
library(stringr)
Ulysses<- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")

str_split(Ulysses , boundary("word"))

splitUlysses <- str_split(Ulysses , boundary("word"))

##Then, extract every third element of this vector.

vector_Ulysses <- unlist(splitUlysses)

third <- vector_Ulysses[seq(from=1, to=22, by=3 )]

third
```

##Challenge 2
```{r Subsetting}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)

##Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x
 y<- c(2,3,6)
 x <- m[ ,y]
 x
 
 ##Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x
 x <- m[6:8, ]
 x
 
 ##Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
 x <-m[2:6, 2:9]
 x
 ##Is this what he wants, or do I need to add the partial columns in 1 & 6?
```

##Challenge 3
```{r Arrays}
##Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)
a<- array(data=400:1, dim=c(5,5,4,4))
a

##Given this matrix, what would the following return?

a[1, 1, 1, 2]
#300

a[2, 3, 2, ]
#364 264 164  64

a[1:5, 1:5, 3, 3]

# 150  145  140  135  130
# 149  144  139  134  129
# 148  143  138  133  128
# 147  142  137  132  127
# 146  141  136  131  126
```

##Challenge 4
```{r Lists}
Platyrrhini<- list("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini<- list("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea<-list(Platyrrhini, Catarrhini)

Tarsioidea<-list("Tarsiidae")

Haplorhini<- list(Anthropoidea, Tarsioidea)

Lorisoidea<- list("Lorisidae", "Galagidae")
Lemuroidea<- list("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")

Strepsirhini<- list(Lorisoidea, Lemuroidea)

Primates<- list(Haplorhini, Strepsirhini)
Primates
##I want a better way to show this--need to do
```

##Challenge 5
```{r Data Frames}
##Store the following numbers as a 5 x 3 matrix: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROWWISE.
matrix<-matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2),nrow=5, ncol=3, byrow= TRUE)

##Coerce the matrix to a data frame.
matrix<- as.data.frame(matrix)

##As a data frame, coerce the second column to be logical-valued
matrix[,2]<-as.logical(matrix[,2])


##As a data frame, coerce the third column to be factor-valued
matrix[,3]<-as.factor(matrix[,3])

##When you are done, use the str() command to show the data type for each variable in your dataframe
str(matrix)
```
 ##Top 5 Challenges
 ###1
 I had trouble in challenge 4 with trying to find a way to show the data.
 
 ###2
 I had issues with the first challenge until I got the proper package actually loaded so it would work/run 
 
 ###3
 I needed to google a bit to find the way to unlist the Ulysses phrase into a vector
 
 ###4
 I also had a weird issue with the Rmarkdown file in general. I kept having issues closing the chunks. At one point I had to compleatly remove one and then remake it. Not sure why?
 
 ###5
 Im not sure on annotating code. I basically just used the challenges themself, but im not sure if it is enough information.